Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration

### 2013-10-11 fixed_speed_theorems.tex
Fix final thm.

Looking at Equation \ref{eq:r-diff}

\begin{align*}
  r(t_b)& = r(t_b-\epsilon) - \bar{v} \int_{t' = T_0}^{t} \cos(\abs{\theta(t')}) dt'
\end{align*}

Since $\cos(\abs{\theta_1(t)}) \ge \cos(\abs{\theta_2(t)})$, $r_1(t_b) \le r_2(t_b)$, so we can invoke Conjecture \ref{conj:optimal-position} to show that $\gamma_1$ is a fastest path which finishes the proof.
\end{proof}

>>>>

Looking at Equation \ref{eq:theta-diff}

\begin{align*}
  \abs{\theta(t_b)}& = \abs{\theta(t_b - \epsilon)} + \int_{t' = t_b-\epsilon}^{t_b} \paren{\frac{\bar{v}}{r(t)} \sin(\abs{\theta(t)}) - \frac{a_c(t)}{\bar{v}}} dt'\\
  \intertext{Now we can find the difference of the two $\theta$'s and take the limit as $\epsilon \to 0$}
  \abs{\theta_2(t_b)} - \abs{\theta_1(t_b)}& \to \int_{t' = t_b-\epsilon}^{t_b} - \frac{a_{c,2}(t) - a_{c,1}(t)}{\bar{v}} dt' \quad \text{as} \quad \epsilon \to 0\\
  & \ge 0 \quad \text{as} \quad \epsilon \to 0
\end{align*}

Furthermore,

\begin{align}
  r(t_b)& = r(t_b - \epsilon) + \int_{t' = t_b - \epsilon}^{t_b} - v(t') \cos(\abs{\theta(t')}) dt'\\
  \intertext{Taking the limit of the difference again}
  r_2(t_b) - r_1(t_b)& \to \int_{t' = t_b - \epsilon}^{t_b} - v(t') \paren{\cos(\abs{\theta_2(t')}) - \cos(\abs{\theta_1(t')})} dt' \quad \text{as} \quad \epsilon \to 0\\
  \intertext{We know that $\theta_2(t_b) \ge \theta_1(t_b)$ as $\epsilon \to 0$, so}
  r_2(t_b) - r_1(t_b)& \ge 0 \quad \text{as} \quad \epsilon \to 0
\end{align}

Now we can invoke Conjecture \ref{conj:optimal-position} to show that $\gamma_1$ is a faster path than $\gamma_2$, which finishes the proof.
\end{proof}
